Community comparison

### 2020-01-11 code/exploratory/community.Rmd
major reorg

```{r rotated-stacked-bar, echo=F, fig.width=7, fig.height=5}

# specify factor order, so Chlainomonas always on same side, etc
species_colors <- c("Chlainomonas A"="#ac71b5","Chlainomonas rubra"="#ac71b5", #purple
                "Sanguina B"="#ff534a", "Sanguina nivaloides"="#ff534a", #red
                # Chloromonas: pastel greens / blues / yellows
                "Chloromonas krienitzii"="#ffa54c","Chloromonas muramotoi C"="#87b1d4", "Chloromonas D"="#94cf92", "Chloromonas F"="#fdfd96", 
                #    orange green                                      pale blu,                   blue green      yellow--only high elev
                "Chloromonas cf. brevispina"="#80c786", "Chloromonas cf. nivalis"="#4aaf86", 
                #                 lt green                            teal
                "Other Chloromonas"="#4aaf53", "Chloromonas"="#4aaf53", 
                # greyish light green
                "Trebouxiophyceae G"="#6a2d2f", "Trebouxiophyceae"="#6a2d2f", # maroon, standout
                "Unknown E"="grey60", "Green cell"="#4aaf53", "Other"="grey60") #greys

# teal #69c095
# medium blue #6994c0

@@

# plot
stacked_bar <- ggplot(combined, aes(x=alias %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=species %>% fct_relevel(names(species_colors))), position="stack", stat="identity") +
  coord_flip() +
  facet_grid(cols = vars(marker %>% fct_relevel(c("Cell morphology","18S","rbcL"))), 
             scales="free_y", space="free_y") +
  theme_classic() +
  labs(x="Sample ID", y="Relative abundance")+
  scale_fill_manual(values = species_colors)

@@

ggsave(here::here("manuscript/figs/stack.pdf"), plot=stack_no_legend, width=7, height=5)
ggsave(here::here("manuscript/figs/stack_legend.pdf"), plot=legend, width=7, height=5)

>>>>

```{r rotated-stacked-bar, echo=F}

# specify factor order, so Chlainomonas always on same side, etc
species_colors <- c("Chlainomonas A"="#ac71b5","Chlainomonas rubra"="#ac71b5", #purple
                "Sanguina B"="#ff534a", "Sanguina nivaloides"="#ff534a", #red
                # Chloromonas: pastel greens / blues / yellows
                "Chloromonas krienitzii"="#ffa54c","Chloromonas muramotoi C"="#87b1d4", "Chloromonas D"="#94cf92", "Chloromonas F"="#fdfd96", 
                #    orange green                                      pale blu,                   blue green      yellow--only high elev
                "Chloromonas cf. brevispina"="#80c786", "Chloromonas cf. nivalis"="#4aaf86", 
                #                 lt green                            teal
                "Other Chloromonas"="#4aaf53", "Chloromonas"="#4aaf53", 
                # greyish light green
                "Trebouxiophyceae G"="#975c5c", "Trebouxiophyceae"="#975c5c", # brown
                "Unknown E"="grey60", "Green cell"="#4aaf53", "Other"="grey60") #greys

@@

# plot  facet_grid(rows = vars(marker %>% fct_relevel(c("Cell morphology","18S","rbcL"))), scales="free_x", space="free_x") +
stacked_bar <- ggplot(combined, aes(x=alias %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=species %>% fct_relevel(names(species_colors))), position="stack", stat="identity") +
  # coord_flip() +
  facet_grid(rows = vars(marker %>% fct_relevel(c("rbcL","18S", "Cell morphology")))) +
  theme_classic() +
  labs(x="Sample ID", y="Relative abundance", fill="Taxa")+
  scale_fill_manual(values = species_colors) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

@@

ggsave(here::here("manuscript/figs/main/community/stack2.pdf"), plot=stack_no_legend, width=7, height=5)
ggsave(here::here("manuscript/figs/main/community/stack2_legend.pdf"), plot=legend, width=7, height=5)
ggsave(here::here("manuscript/figs/main/community/stack_full.pdf"), plot=stacked_bar, width=180, height=180, units = "mm", dpi=300)
